Nested Sampling with Multiple Objective Functions

### 2018-06-15 doc/ms.tex
Bunch of work on the paper

\section{Example 1: Known solution}
In the software repository, this example is implemented in
{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
\end{eqnarray}
The second objective function, given by
\begin{eqnarray} 
E_2(\xx) &=& \sin^2(10 \pi x_i),
\end{eqnarray}
upweights states where coordinates $\{x_i\}$
are close to 0, 0.1, 0.2, ..., 0.9 and 1.
The canonical distributions for this system should draw the coordinates
towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
relative importance of these effects determined by the values of the
inverse temperatures $\beta_1$ and $\beta_2$. Three example canonical
distributions are shown in Figure~\ref{fig:demo_canonical}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.75]{figures/demo_canonical.pdf}
\caption{Three canonical distributions for different values of the two
temperatures $T_1$ and $T_2$. These are for the one-dimensional case, but
in this example, the 100 dimensional canonical distributions are independent
and have these distributions as their marginals.\label{fig:demo_canonical}}
\end{figure}

The true partition function (computed numerically) and the Kullback-Leibler
divergence from the prior to the canonical distribution are shown in
Figure~\ref{fig:demo_truth} as a function of two temperatures.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.75]{figures/demo_truth.pdf}
\caption{The true partition function and KL divergence (from the prior to
the canonical distribution) as a function of two temperatures for the
test problem.\label{fig:demo_truth}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y. and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing—Original Draft Preparation, X.X.; Writing—Review \& Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.'', please turn to the \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Please add: ``This research received no external funding'' or ``This research was funded by [name of funder] grant number [xxx].'' Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g. materials used for experiments).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}

@@

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

>>>>

\section{Example 1: Known solution}
In the software repository, this example is implemented in
{\tt examples/Demo.h} and {\tt examples/Demo.cpp}.
We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distributions are iid normal centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
E_1(\xx) &=& \sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.1}\right)^2.
\end{eqnarray}
The second objective function, given by
\begin{eqnarray} 
E_2(\xx) &=& \sin^2(10 \pi x_i),
\end{eqnarray}
upweights states where coordinates $\{x_i\}$
are close to 0, 0.1, 0.2, ..., 0.9 and 1.
The canonical distributions for this system should draw the coordinates
towards 0.5 (due to $E_1$) and towards the troughs of $E_2$, with the
relative importance of these effects determined by the values of the
inverse temperatures $\beta_1$ and $\beta_2$. Three example canonical
distributions are shown in Figure~\ref{fig:demo_canonical}.
The true partition function (computed numerically) and the Kullback-Leibler
divergence from the prior to the canonical distribution are shown in
Figure~\ref{fig:demo_truth} as a function of two temperatures. These show the
common behaviour where lower temperatures correspond to lower values
of the normalising constant $\log Z$ and higher values of the KL divergence
$H$. There are no phase changes, which would result in discontinuities.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figures/demo_canonical.pdf}
\caption{Three canonical distributions for different values of the two
temperatures $T_1$ and $T_2$, in the simple demo problem.
These are for the one-dimensional case, but
in this example, the 100 dimensional canonical distributions are `independent
and identically distributed' version of this distribution.
Low values of $T_1$ bring
more probability towards the centre of the domain, and low values of $T_2$
bring out the oscillatory structure in the probability density function.
\label{fig:demo_canonical}}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figures/demo_truth.pdf}
\caption{The true partition function and KL divergence (from the prior to
the canonical distribution) as a function of two temperatures for the
test problem.\label{fig:demo_truth}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{BJB conceived the problem and worked on various ideas
over the years that nearly worked. RJNB suggested and worked on the polymer
example.
EC discussed the problem and worked on
several attempts at solutions with BJB over the years.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{This research received no external funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{BJB acknowledges research and study leave funding from the
University of Auckland. We would like to thank Gabor Csanyi, Livia B. Partay,
Rob Salomone, John Skilling, etc etc.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest.}

@@

\noindent 
\begin{tabular}{@{}ll}
MCMC & Markov Chain Monte Carlo \\
NS & Nested Sampling \\
SMC & Sequential Monte Carlo
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{yes} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{one} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{Using the TwinPeaks2018 software}

%\section{}
%All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\sampleavailability{Samples of the compounds ...... are available from the authors.}
